Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654

### 2016-05-17 WRITEUP/ms.tex
done writing origin of CO21, and claim is wet-wet merger

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results
%
%
%
%
%
\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of $\sigma$ = 1.
451mJy per channel beam\pmOne.
Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
limit of 4.353 mJy \kms beam\pmOne.

\susbsection{Origin of the \bco emission} \label{sec:origin}

gas:
CO is from the optical QSO, because co-spatial with the lensed optical emission, but also emisson from the companion.
We adopt the ULIRG value, as used in the largest samples of non-local ULIRGs (solomon+97, Combes+11).
We classify this as wet-wet merger given a contribution of CO from the companion. However, we cannot quantify this with a mass ratio given the spatial resolution. This will be verified in further higher-resolution observations.

\subsection{\bco kinematics}

\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling}
With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.

>>>>

% Done: PdBI observations, VLA observations, CARMA obs, HST astrometry, CO21 results, origin of \bco
%
%
%
%
%
\documentclass[]{emulateapj}
\usepackage{amsmath}
\input{preamble}
\slugcomment{To be submitted to the ApJ}

@@

We place an upper limit on \rot[HNC]{2}{1} line emission at the red-shifted
frequency 140 GHz in the foreground galaxy at $z\sim$0.295) of
$\sigma$ = 1.451mJy per channel beam\pmOne.
Assuming a typical line width of 300 \kms, this corresponds to a 3$\sigma$
limit of 4.353 mJy \kms beam\pmOne.

\susbsection{Origin of the \bco emission} \label{sec:origin} %DONE
Evidently, the CO emission is co-spatial with the lensed optical emission in
the background AGN host galaxy. The question is then whether the optically
faint companion also contributes to the CO flux and thus contains a
non-negligible amount of molecular gas.
Indeed, based on our lens model presented in \Sec{lensmodel}, we find it
highly likely that part of the CO emission originates from
the companion. We thus classify RXJ1131 as a ``wet-wet'' merger.
However, we cannot quantify this with a mass ratio given the
spatial resolution. This will be verified in future higher-resolution observations. In the subsequent sections, we will interpret RXJ1131
using this scenario (i.e. a ``wet-wet'' merger).

\subsection{\bco kinematics}
\begin{figure}[!htbp]
\centering
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/{F555WCO21_mom0_single.invertedgray}.eps}
\includegraphics[trim=0 5 0 15, clip, width=0.25\textwidth]{../Figures/F555W_REDBLUE.eps}
\includegraphics[width=0.5\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\caption{
Contours for the first (left) and second (right) moment maps are shown in steps of 50 \kms, and 100 \kms, respectively. The beam (native resolution) is shown in the right panel.
\label{fig:CO21highO}}
\end{figure}

@@

%--------------------------------------------------------------------------
%                                Analysis
%--------------------------------------------------------------------------
\section{Analysis}
\subsection{Lens modeling} \label{lensmodel}
With the high SNR and spectral resolution, we model different kinematic components using our lensing code \uvmcmcfit.
